### 2017-10-10 paper/sexSelectionSpacing-ver1.tex
Minor edits

\date{September 2017\\
\bigskip
Preliminary}

@@

% Demography abstract
\noindent This paper examines how birth spacing interact with the use of 
sex-selective abortions. 
I introduce a statistical method that incorporates that sex-selective abortions 
affect both the likelihood of a son and spacing between births.
Using India's National Family and Health Surveys,
I show that use of sex selection leads to \emph{longer} spacing after a daughter 
is born than after a son, but for families that do not use sex selection
duration to next birth is still shorter when no boys are present.
Women with 8 or more years of education, both in urban and rural areas, are 
the main users of sex-selective abortions, whereas women with less education 
do not appear to use sex selection.

>>>>

\date{October 2017\\
\bigskip
Preliminary}

@@

% Demography abstract
\noindent This paper examines how birth spacing interact with the use of 
sex-selective abortions. 
I introduce a statistical method that incorporates that sex-selective abortions 
affect both the likelihood of a son and spacing between births.
Using India's National Family and Health Surveys,
I show that use of sex selection leads to \emph{longer} spacing after a daughter 
than after a son, but for families that do not use sex selection
duration to next birth is still shorter when no boys are present.
Women with 8 or more years of education, both in urban and rural areas, are 
the main users of sex-selective abortions, whereas women with less education 
do not appear to use sex selection.
